On first-order combinatorial proofs

### 2020-11-24 main.tex
Finish a proof

\parindent=0pt

@@

@@

If $G_i = \forall x H_i$ for some $i$, then there will a conjunction of $U_x*$
and some formula which can never be eliminated by the rules $\me$, $\me'$ and
$\acD$. However, there exists no such conjunction in ${A^P}^*$, which leads to a
contradiction.

@@

\end{proof}	
\end{lemma}
\end{document}

>>>>

\parindent=0pt
\parskip=0.6em

@@

First consider the $\acD$ rule:
\begin{prooftree}
  \hypo{C \vee C}
  \infer1[$\acD$]{C}
\end{prooftree}

It is clear that if $C$ is a propositional encoding, then so is $C \vee C$.

@@

If $G_i = \forall x H_i$ for some $i$, then there will a conjunction of $U_x^*$
and some formula which can never be eliminated by the rules $\me$, $\me'$ and
$\acD$. However, there exists no such conjunction in ${A^P}^*$, which leads to a
contradiction.

@@

Finally, consider the $\me'$ rule:

Suppose that $Q_X^* \wedge (C \vee D)$ = $F^P$ for some $P$. It is clear
that $Q_x^* = E_x^*$ and $F = \exists x G$ with $G^P = C \vee D$ for some $G$.
We distinguish two cases:
\begin{itemize}
  \item $G = \forall y H$: in this case, $(Q_x^* \wedge C) \vee (Q_x^* \wedge
D)$ has a subformula $(E_x^* \wedge U_y^*)$, which cannot be eliminated by the
rules $\me$, $\me'$, $\acD$. It is clear that ${A^P}^*$ does not
have a subformula of this form, which leads to a contradiction.
  \item $G = G_1 \vee G_2$: in this case, $(Q_x^* \wedge C) \vee (Q_x^* \wedge
	  D) = ((\exists x G_1) \vee (\exists x G_2))^P$.
\end{itemize}

\end{proof}	
\end{lemma}

\end{document}
